Intelligent Building Energy Management System

### 2021-05-01 parts/10-introduction.tex
Initial feedback by Dr. Miah

\section{Project Description}
The Internet of Things is a large network of embedded devices like sensors, wearables, and appliances capable of receiving control commands and reporting data over the Internet. Many industries take advantage of this infrastructure to improve process flow and efficiency. One of these industries is the commercial and industrial sector which often employ building automation or management systems to help better manage processes or devices in a building like air conditioning systems, lights or industrial machines. Technological advancements have allowed devices to become connected to a building network through communication protocols like WiFi, Ethernet, Modbus, or BACnet which enables them to be more easily controlled from a central system.
\medbreak\noindent
Our overall goal is to create a platform in which users can login and access devices connected to a building's energy supply. This will allow the user to closely monitor energy usage throughout a commercial or residential building. Additionally, the user will be able to control devices connected to the platform, allowing precise control over the building's energy use. The minimum viable product of this project will be to connect to 1 to 3 devices via the the platform and control them.

@@

During a research project with Dr. Miah, the DC motor interface was successfully implemented into the BEMOSS platform which required adding a great deal of code to the platform to fully implement the device as BEMOSS does not support adding new devices currently. The research also consisted of adding a new logo to the platform for the motor. A possible improvement our platform will make is helping developers on the project to add new devices more easily.

One of the improvements our project makes over the previous is the use of UDP multicasting which does not require any superuser privileges to locate an embedded computer (Beaglebone Blue). This implementation is also more convenient because it does not require installing any packages as multicasting is natively supported by most embedded Linux systems. If in the future, multiple embedded computers are needed to be discovered, the multicasting system works elegantly as each device can simply listen on a provided multicast group which consists of an IP address and port number.

@@

One such platform is BEMOSS from the Virginia Polytechnic Institute and State University Advanced Research Institute. BEMOSS features include being open-source, allowing for multiple communication technologies, and supporting many common IoT devices. This system allows for monitoring and controlling a variety of devices securely.

Another open-source platform is rEMpy or residential Energy Management in python. The main focus of this platform developed by a team of researchers at Universit\`{a} Politecnica delle Marche in Ancona, Italy was to simulate the energy flow of a residential home. With the data collected from simulations, it was possible for them to use forecasting and prediction algorithms to predict various quantities like energy usage and power consumption over a given time period. Their energy management system consists of a well-defined structure with components like a user interface, database, and optimal scheduler that communicates with modules like a prediction and thermal model. In terms of software technologies, it uses the Django web framework which provides a lot of built-in functionality for web development like a user-authentication system and object-relational mapping. Adapting the project to this framework could be a great way to help improve security and optimize database queries \cite{fagiani2017}.

@@

In~\cite{8246800}, the authors describe similar functional requirements to our own BEMS Core. They periodically gather power consumption and device status data and send that data to a database. We are doing exactly what they describe using the Apache Cassandra database. The authors also use an "analytics [sic] engine to process [the data] and generate reports, graphs, and charts." Our system only generates a power consumption plot for a given day, but we are still meeting this same requirement - just on a smaller scale. The communication with devices and power consumption reports are to be accessible through a web-based application that is easy to use. Again, our implementation is simple and very intuitive for the end-user. Finally, these authors mention a user-login feature. They explain that their system would include multiple levels of accessibility based on the user privileges. Although our system does not currently have a user-login feature, it simply uses a router to access devices that are also connected to the router. Since this is a closed system, users need only protect their router with a secure password.

A control scheme in~\cite{Barchi2018} is presented to manage a photovoltaic array and battery energy storage system. Tests were conducted in a shopping mall with an electronic load to emulate the power consumption of the building. Potentially, a similar technique could be used to model the energy demand of a house in Simulink or Simscape model. Through their scheme, an intelligent BEMS is used to collect measurable data like power, voltage, and current and stored for offline analysis later. Their platform collects data every five minutes compared to the 20 second polling rate currently configured in our platform. A control algorithm was presented proving that grid energy is consumed more heavily during periods of low power demand rather than PV power.

@@

%----------------------------------------------------------------------
\section{Report Organization}
%----------------------------------------------------------------------
This report is organised into 5 chapters.  Chapter \ref{ch: Chapter1} discusses what this project hopes to accomplish and what similar projects have completed. Chapter \ref{ch: Chapter2} explains the architecture. Chapter \ref{ch: Chapter3} provides a brief explanation of the control algorithms and architectures used. Chapter \ref{ch: Chapter4} contains the results from our simulations. Chapter \ref{ch: Chapter5} concludes the paper and provides insight into future directions.

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../finalReportMainV1"
%%% End:

>>>>

\section{Project Description}
The Internet of Things is a large network of embedded devices
\replace{like}{, such as} sensors,
wearables, and appliances capable of receiving control commands and reporting
data over the Internet. Many industries take advantage of this infrastructure to
improve process flow and efficiency. One of these industries is the commercial
and industrial sector which often employ building automation or management
systems to help better manage processes or devices in a building like air
conditioning systems, lights or industrial machines. Technological advancements
have allowed devices to become connected to a building network through
communication protocols like WiFi, Ethernet, Modbus, or BACnet which enables
them to be more easily controlled from a central system.

Our overall goal is to create a platform in which users can login and access devices
connected to a building's energy supply. This will allow the user to closely
monitor energy usage throughout a commercial or residential building.
Additionally, the user will be able to control devices connected to the
platform, allowing precise control over the building's energy use. The minimum
viable product of this project will be to connect to 1 to 3 devices via the the
platform and control them.

@@

During a research project led by Miah \textit{et al.,} the DC motor interface was successfully
implemented into the BEMOSS platform which required adding a great deal of
\add{source} code
to the platform to fully implement the device as BEMOSS does not support adding
new devices currently. The research also consisted of adding a new
\add{features, such as } logo to the
platform for the motor. A possible improvement our platform will make is helping
developers on the project to add new devices more easily.

One of the improvements our project makes over the previous is the use of UDP
\add{(user datagram protocol)} multicasting which does not require any superuser privileges to locate an
embedded computer (Beaglebone Blue\add{, for example}). This implementation is also more convenient
because it does not require installing any packages as multicasting is natively
supported by most embedded Linux systems. If in the future, multiple embedded
computers are needed to be discovered, the multicasting system works elegantly
as each device can simply listen on a provided multicast group which consists of
an IP address and port number.

@@

One such platform is the BEMOSS from the Virginia Polytechnic Institute and State
University Advanced Research Institute. BEMOSS features include being
open-source, allowing for multiple communication technologies, and supporting
many common IoT devices. This system allows for monitoring and controlling a
variety of devices securely\todo[inline]{Need citation here}.

Another open-source platform is rEMpy or residential Energy Management in
Python. The main focus of this platform developed by a team of researchers at
Universit\`{a} Politecnica delle Marche in Ancona, Italy was to simulate the
energy flow of a residential home. With the data collected from simulations, it
was possible for them to use forecasting and prediction algorithms to predict
various quantities \replace{like}{, such as} energy usage and power consumption over a given time period. Their energy management system consists of a well-defined structure with components like a user interface, database, and optimal scheduler that communicates with modules like a prediction and thermal model. In terms of software technologies, it uses the Django web framework which provides a lot of built-in functionality for web development like a user-authentication system and object-relational mapping. Adapting the project to this framework could be a great way to help improve security and optimize database queries~\cite{fagiani2017}.

@@

In~\cite{8246800}, \remove{the }authors describe similar functional requirements to our
own BEMS Core. They periodically gather power consumption and device status data
and send that data to a database. We are doing exactly what they describe using
the Apache Cassandra database. The authors also use an "analytics [sic] engine
to process [the data] and generate reports, graphs, and charts." Our system only
generates a power consumption plot for a given day, but we are still meeting
this same requirement - just on a smaller scale. The communication with devices
and power consumption reports are to be accessible through a web-based
application that is easy to use. Again, our implementation is simple and very
intuitive for the end-user. Finally, these authors mention a user-login feature.
They explain that their system would include multiple levels of accessibility
based on the user privileges. Although our system does not currently have a
user-login feature, it simply uses a router to access devices that are also
connected to the router. Since this is a closed system, users need only protect
their router with a secure password.

A control scheme in~\cite{Barchi2018} is presented to manage a photovoltaic
array and battery energy storage system. Tests were conducted in a shopping mall
with an electronic load to emulate the power consumption of the building.
Potentially, a similar technique could be used to model the energy demand of a
house in Simulink or Simscape model. Through their scheme, an intelligent BEMS
is used to collect measurable data \replace{like}{, such as} power, voltage, and current and stored for offline analysis later. Their platform collects data every five minutes compared to the 20 second polling rate currently configured in our platform. A control algorithm was presented proving that grid energy is consumed more heavily during periods of low power demand rather than PV power.

@@

%----------------------------------------------------------------------
\section{Report Organization}
%----------------------------------------------------------------------
This report is organised into 5 chapters.  Chapter \ref{ch: Chapter1} discusses
what this project hopes to accomplish and what similar projects have completed.
Chapter \ref{ch: Chapter2} explains the architecture. Chapter \ref{ch: Chapter3}
provides a brief explanation of the control algorithms and architectures used.
Chapter \ref{ch: Chapter4} contains the results from \replace{our simulations}{a
few experiments}. Chapter \ref{ch: Chapter5} concludes the \replace{paper}{report} and provides insight into future directions.

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../finalReport"
%%% End:

### 2021-05-01 parts/20-iBEMSArchitecture.tex
Initial feedback by Dr. Miah

\begin{figure}[H]
    \centering
    \includegraphics[scale=0.8]{figs/highLevelArchitecture.pdf}
    \caption{High Level Architecture of the Proposed System}
    \label{fig:highLevelArchitecture}
\end{figure}

At the center of the iBEMS architecture is the iBEMS core. This core interacts with multiple peripherals including IoT devices and a weather API over the internet. Over the course of this project, we managed to develop support for 2 IoT devices displayed in Figure~\ref{fig:highLevelArchitecture}. These devices are the WeMo Insight Switch and an embedded computer known as the Beaglebone Blue. Our initial plan for the smart meter shown in Figure~\ref{fig:highLevelArchitecture} was to use it in a Simscape model of a microgrid. However, we did not list this as a requirement for the project, so we decided not to implement it due to time constraints. The core is also able to connect the internet to download weather data for Peoria, Illinois through OpenWeatherMap.

\section{Low Level Architecture}
\begin{figure}[H]
    \centering
    \includegraphics[scale=0.8]{figs/functionalBlockDiagram.pdf}
    \caption{Functional Block Diagram}
    \label{fig:functional_bd}
\end{figure}

Figure~\ref{fig:functional_bd} gives lower level detail on the system architecture. The inputs include the user input through the web server, the device status updates (On/Off, power usage, etc...) and the weather data. The iBEMS Core itself consists of a Flask Web Server, 2 databases (Apache Cassandra and SQLite), and 3 software agents (Discovery, Control, and Scheduling).
\medbreak
The Flask web server is built using a Python web framework titled Flask which allows programmers to develop a dynamic web server capable of rendering data to HTML pages. The benefit of this framework over other Python web frameworks like Django is the large amount of customization available. For example, the developers can create a completely custom user login system. For now, the server is capable of being accessed only on the server computer running Ubuntu Linux. In the future, support could be added to allow any user on the LAN to access the web server. Other web frameworks use object relational mapping directly to access the relevant databases. However, our system uses direct queries with both SQLite and the Cassandra query language to query the database.
\medbreak
We used 2 different databases to store information on. The Apache Cassandra database was better suited for the time series data such as device status and power usage. This database was therefore utilized a lot by the Control and Scheduling Agents. The SQLite database hold parameters that do not change over time like device ID's, IP addresses, and MAC addresses which made it amendable to the processes in the Discovery Agent. A possible improvement to this project could be to only utilize 1 database for development simplicity.
\medbreak
The first agent that is used by the iBEMS Core on startup is the discovery agent. It is responsible for reaching out on the network and finding all devices that the iBEMS Core has support for. This process involves retrieving the following parameters: IP address, Port number, MAC address, Manufacturer, Name, and API.
Once all available devices are connected, the Control agent is used to change the status of each device and collect power usage data in real time. Finally, the scheduling will take input from the user and place the corresponding scheduling periods in the Apache Cassandra database. Then, a thread is created to poll the current device status at regular intervals and updates the status if it does not match the defined status in the Apache Cassandra database.

\begin{figure}[H]
    \centering
    \includegraphics[scale=0.6]{figs/overallDiagram.pdf}
    \caption{Interconnection between system components}
    \label{fig:systemComponentInterconnection}
\end{figure}

Figure~\ref{fig:systemComponentInterconnection} provides an explanation of how the components of the system interact with each other. The Apache Cassandra database and SQLite database are accessible from the web server, control agent, discovery agent, and scheduling agent. The web server queries the time series database and metadata database for vastly different purposes. Power plotting requires querying the Apache Cassandra database. To distinguish between the different devices on the front end, the metadata database is used. The agents utilize the Apache Cassandra database for storing and extracting time-series data. The agents use the metadata database to distinguish between different devices.

@@

\begin{figure}[H]
    \centering
    \includegraphics[scale=0.9]{figs/operationalModes.pdf}
    \caption{Operation Modes Interaction}
    \label{fig:functional_bd}
\end{figure}

There are 5 general modes of operation in iBEMS. In Mode 0, before iBEMS is even launched, the user must open the Startup Menu, which is a desktop graphical user interface (GUI). This is a simple GUI with only 2 buttons for starting and stopping iBEMS. Upon clicking "Start iBEMS," the login page will load where the user can enter a valid username and password to use iBEMS. Once a valid username and password is entered, the home screen will be shown which displays the weather data being downloaded from the OpenWeatherMap API. This information include temperature in Fahrenheit and Celsius, wind speed in MPH, humidity, and cloud coverage. At this point, a navigation bar is available to view "Active Devices" page and the "Scheduling" page. "Active Devices" corresponds to Mode 3 for controlling devices in real time. The user will also be able to view power plots in this mode as well. Lastly, the "Scheduling" page is Mode 4 for creating schedules for all connected devices.

@@

\begin{circuitikz}[american]
    \tikzstyle{every node} = [font = \tiny]
      % \usetikzlibrary{patterns}
      \draw
      (0,0) to[sqV,invert,l=Motor Drive Voltage from H-Bridge] ++(0,4*\smgrid)
      to[Telmech=M,n=motor,fill=red!20] ++(4*\smgrid,0)
      to[C,l=$1~{[}\mu F{]}$,*-*] ++(0,-4*\smgrid) to[short]++(-4*\smgrid,0); 
      \draw
      (4*\smgrid,4*\smgrid) to[short,-*]++(3*\smgrid,0)
      to[short,-o]++(2*\smgrid,0)node[right]{Embedded Computer ADC (Ch\#0)};
      \draw
      (7*\smgrid,4*\smgrid) to[R,l=$2~{[}\Omega{]}$,-*]++(0,-4*\smgrid)
      to[short]++(-4*\smgrid,0);
      \draw
      (7*\smgrid,0) to[short,-o]++(2*\smgrid,0) node[right]{Embedded
        Computer ADC (Ground)};
\end{circuitikz}

A large feature of this project was being able to record power usage from the connected IoT devices. The embedded computer does not have a built-in capability to measure its own power usage, so this circuit was needed to make that possible. Essentially, this circuit will measure the current being used to drive one of the motors on the robot chassis. The on-board Analog-to-Digital-Converter (ADC) can be used to read the voltage across the resistor and since the resistance is known, the current can be calculated as $I = V/R$. Also, the voltage from the H-Bridge to drive the motors on the embedded computer is known so the power consumed by 1 motor is $Motor Drive Voltage * I$. For the specific robot chassis used in this project, there are 4 motors, so multiplying the power found from this circuit by 4 will give an approximation of the total power used by the robot. For other robots with different power sources besides a Lipo battery,

@@

>>>>

At the center of the iBEMS architecture is the iBEMS core. This core interacts
with multiple peripherals including IoT devices and a weather API over the
internet. Over the course of this project, we managed to develop support for 2
IoT devices displayed in Figure~\ref{fig:highLevelArchitecture}. %
%
\begin{figure}
  \centering
  \includegraphics[scale=0.3]{figs/highLevelArchitecture.pdf}
  \caption{High Level Architecture of the Proposed System}
  \label{fig:highLevelArchitecture}
\end{figure}
%
These devices are the WeMo Insight Switch and an embedded computer known as the Beaglebone
Blue. Our initial plan for the smart meter shown in
Figure~\ref{fig:highLevelArchitecture} was to use it in a Simscape model of a
microgrid. However, we did not list this as a requirement for the project, so we
decided not to implement it due to time constraints. The core is also able to
connect the internet to download weather data for Peoria, Illinois through
OpenWeatherMap.

\section{Low Level Architecture}

Figure~\ref{fig:functional_bd} gives lower level detail on the system
architecture. %
%
\begin{figure}
  \centering
  \includegraphics[scale=0.3]{figs/functionalBlockDiagram.pdf}
  \caption{Functional Block Diagram}
  \label{fig:functional_bd}
\end{figure}
%
The inputs include the user input through the web server, the device status
updates (On/Off, power usage, etc...) and the weather data. The iBEMS Core
itself consists of a Flask Web Server, 2 databases (Apache Cassandra and
SQLite), and 3 software agents (Discovery, Control, and Scheduling).

The Flask web server is built using a Python web framework titled Flask which
allows programmers to develop a dynamic web server capable of rendering data to
HTML pages. The benefit of this framework over other Python web frameworks like
Django is the large amount of customization available. For example, the
developers can create a completely custom user login system. For now, the server
is capable of being accessed only on the server computer running Ubuntu Linux.
In the future, support could be added to allow any user on the LAN to access the
web server. Other web frameworks use object relational mapping directly to
access the relevant databases. However, our system uses direct queries with both
SQLite and the Cassandra query language to query the database. \medbreak We used
2 different databases to store information on. The Apache Cassandra database was
better suited for the time series data such as device status and power usage.
This database was therefore utilized a lot by the Control and Scheduling Agents.
The SQLite database hold parameters that do not change over time like device
ID's, IP addresses, and MAC addresses which made it amendable to the processes
in the Discovery Agent. A possible improvement to this project could be to only
utilize 1 database for development simplicity. \medbreak The first agent that is
used by the iBEMS Core on startup is the discovery agent. It is responsible for
reaching out on the network and finding all devices that the iBEMS Core has
support for. This process involves retrieving the following parameters: IP
address, Port number, MAC address, Manufacturer, Name, and API. Once all
available devices are connected, the Control agent is used to change the status
of each device and collect power usage data in real time. Finally, the
scheduling will take input from the user and place the corresponding scheduling
periods in the Apache Cassandra database. Then, a thread is created to poll the
current device status at regular intervals and updates the status if it does not
match the defined status in the Apache Cassandra database.

Figure~\ref{fig:systemComponentInterconnection} provides an explanation of how
the components of the system interact with each other. %
%
\begin{figure}
  \centering
  \includegraphics[scale=0.6]{figs/overallDiagram.pdf}
  \caption{Interconnection between system components}
  \label{fig:systemComponentInterconnection}
\end{figure}
%
The Apache Cassandra database and SQLite database are accessible from the web server, control agent, discovery agent, and scheduling agent. The web server queries the time series database and metadata database for vastly different purposes. Power plotting requires querying the Apache Cassandra database. To distinguish between the different devices on the front end, the metadata database is used. The agents utilize the Apache Cassandra database for storing and extracting time-series data. The agents use the metadata database to distinguish between different devices.

@@

\begin{figure}
  \centering
  \includegraphics[scale=0.4]{figs/operationalModes.pdf}
  \caption{Operation Modes Interaction}
  \label{fig:operationalModes}
\end{figure}

There are 5 general modes of operation in iBEMS as shown in Figure~\ref{fig:operationalModes}. In Mode 0, before iBEMS is even launched, the user must open the Startup Menu, which is a desktop graphical user interface (GUI). This is a simple GUI with only 2 buttons for starting and stopping iBEMS. Upon clicking "Start iBEMS," the login page will load where the user can enter a valid username and password to use iBEMS. Once a valid username and password is entered, the home screen will be shown which displays the weather data being downloaded from the OpenWeatherMap API. This information include temperature in Fahrenheit and Celsius, wind speed in MPH, humidity, and cloud coverage. At this point, a navigation bar is available to view "Active Devices" page and the "Scheduling" page. "Active Devices" corresponds to Mode 3 for controlling devices in real time. The user will also be able to view power plots in this mode as well. Lastly, the "Scheduling" page is Mode 4 for creating schedules for all connected devices.

@@

A large feature of this project was being able to record power usage from the
connected IoT devices. The embedded computer does not have a built-in capability
to measure its own power usage, so this circuit was needed to make that
possible. Essentially, this circuit will measure the current being used to drive
one of the motors on the robot chassis. The on-board Analog-to-Digital-Converter
(ADC) can be used to read the voltage across the resistor and since the
resistance is known, the current can be calculated as $I = V/R$. Also, the
voltage from the H-Bridge to drive the motors on the embedded computer is known
so the power consumed by 1 motor is $Motor Drive Voltage * I$. For the specific
robot chassis used in this project, there are 4 motors, so multiplying the power
found from this circuit by 4 will give an approximation of the total power used
by the robot. For other robots with different power sources besides a Lipo
battery. See Figure~\ref{fig:motorInterfaceCircuit} for details of the interface
circuit for computer power usage by the DC motor.

\begin{figure}
  \centering
  \begin{circuitikz}[american]
    \tikzstyle{every node} = [font = \tiny]
    % \usetikzlibrary{patterns}
    \draw
    (0,0) to[sqV,invert,l=Motor Drive Voltage from H-Bridge] ++(0,4*\smgrid)
    to[Telmech=M,n=motor,fill=red!20] ++(4*\smgrid,0)
    to[C,l=$1~{[}\mu F{]}$,*-*] ++(0,-4*\smgrid) to[short]++(-4*\smgrid,0); 
    \draw
    (4*\smgrid,4*\smgrid) to[short,-*]++(3*\smgrid,0)
    to[short,-o]++(2*\smgrid,0)node[right]{Embedded Computer ADC (Ch\#0)};
    \draw
    (7*\smgrid,4*\smgrid) to[R,l=$2~{[}\Omega{]}$,-*]++(0,-4*\smgrid)
    to[short]++(-4*\smgrid,0);
    \draw
    (7*\smgrid,0) to[short,-o]++(2*\smgrid,0) node[right]{Embedded
      Computer ADC (Ground)};
  \end{circuitikz}
  \caption{Interface circuit to calculate power consumption of a DC motor
    running from the embedded computer copmuter.}
  \label{fig:motorInterfaceCircuit}
\end{figure}

@@

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../finalReport"
%%% End:

### 2021-05-01 parts/30-Implementation.tex
Initial feedback by Dr. Miah

% Talk about Zero MQ
All three agents communicate with each other and the web server using the Zero MQ asynchronous messaging library [citation here]. Essentially, this library works as a way to implement inter process communication without a message broker. In other words, different processes are able to communicate with each other without any central bus. This is convenient as fewer processes are needed for the system to function. Lowering the number of overall processes lowers the RAM and CPU usage of the software. The library is ported to many different programming languages; however we are using the Python port titled Pyzmq to implement in our code base. 
\begin{figure}[H]
    \centering
    \includegraphics{figs/pubSubAgents.pdf}
    \caption{Publish Subscribe Communication using ZeroMQ}
    \label{fig:pubSubAgents}
\end{figure}
More specifically, the publish subscribe model of communication is used where each agent communicates via a socket where each socket responds to a specific topic. The topics and port numbers are listed below along with their corresponding agents in Table~\ref{tab:pubsubspecs}.
\begin{table}[H]
    \centering
    \begin{tabular}{|c|c|c|}
        \hline
        Agent & Topic & Port Number\\
        \hline
        Discovery Agent & "discovery" & 5556\\
        Scheduling Agent & "scheduling" & 5556\\
        Control Agent & "control" & 5556\\
        \hline
    \end{tabular}
    \caption{Publish/Subscribe Communication Specifications}
    \label{tab:pubsubspecs}
\end{table}
In order to send data between the different processes, the topic, method, and data are delimited in a particular way. This method is shown below as follows
\begin{verbatim}
    topic method/args
\end{verbatim}
A space cannot be included between the method name and arguments as this interferes with the Python \texttt{split} method for extracting the fields. The \texttt{topic} is the string described previously, the \texttt{method} is the name of the desired method to be called on the agent object, and \texttt{args} is the arguments supplied to the desired method. In order to send a message to an agent, the \texttt{publish} method defined in the \texttt{pubsub} module should be called. An optional argument titled \texttt{cycleCount} is available which will allow the publish message to be sent multiple times. During testing, it was found that during the transmission of some messages, this was necessary due to the way ZeroMQ is implemented.

@@

\subsection{Control Agent Functionality}
The flow chart of method \texttt{setDeviceStatus} is shown in Figure~\ref{fig:setDeviceStatus}. The purpose of this method is to set the status of the desired device. When the method is called, the data dictionary is obtained which contains the device ID. With this device ID, the API type can be determined using the SQLite database. Subsequently, the appropriate device API module can be imported. If the power state exists as a key in the device data dictionary, the power state of the WeMo Insight Switch will be set as ON or OFF. If the duty cycle key exists, the duty cycle of the single board computer motor drivers is set. If the shutdown key is set, the single board computer is shutdown. In order to reconnect to the single board computer, the board must be started and receiver program ran. If necessary, the device must be reconnected to the WiFi network.  
\begin{figure}[H]
    \centering
    \includegraphics[scale=0.5]{figs/setDeviceStatus.pdf}
    \caption{setDeviceStatus Flow Chart}
    \label{fig:setDeviceStatus}
\end{figure}
To obtain necessary data quantities from the device, the \texttt{getDeviceStatus} method is defined. Once the proper data parameters are obtained, the \texttt{getState} function defined in the devices API module can be called with the data parameters like power state and status. Once the agent has finished sending these to the device, a request is sent to the web server to inform the server that it completed searching for the required device data.

\begin{figure}[H]
    \centering
    \includegraphics[scale=0.5]{figs/getDeviceStatus.pdf}
    \caption{getDeviceStatus Flow Chart}
    \label{fig:getDeviceStatus}
\end{figure}

>>>>

% Talk about Zero MQ
All three agents communicate with each other and the web server using the Zero
MQ asynchronous messaging library\todo{citation here}. Essentially, this library
works as a way to implement inter process communication without a message
broker. In other words, different processes are able to communicate with each
other without any central bus. This is convenient as fewer processes are needed
for the system to function. Lowering the number of overall processes lowers the
RAM and CPU usage of the software. The library is ported to many different
programming languages; however we are using the Python port titled Pyzmq to
implement in our code base.
%
\begin{figure}
    \centering
    \includegraphics[width=0.4\textwidth]{figs/pubSubAgents.pdf}
    \caption{Publish Subscribe Communication using ZeroMQ}
    \label{fig:pubSubAgents}
\end{figure}
%
\todo[inline]{Figures are cited in the text}

More specifically, the publish subscribe model of communication is used where
each agent communicates via a socket where each socket responds to a specific
topic. The topics and port numbers are listed below along with their
corresponding agents in Table~\ref{tab:pubsubspecs}. %
%
\begin{table}
    \centering
    \begin{tabular}{|c|c|c|}
        \hline
        Agent & Topic & Port Number\\
        \hline
        Discovery Agent & "discovery" & 5556\\
        Scheduling Agent & "scheduling" & 5556\\
        Control Agent & "control" & 5556\\
        \hline
    \end{tabular}
    \caption{Publish/Subscribe Communication Specifications}
    \label{tab:pubsubspecs}
\end{table}
%
In order to send data between the different processes, the topic, method, and
data are delimited in a particular way. This method is shown below as follows: %
%
\begin{verbatim}
    topic method/args
\end{verbatim}
%
A space cannot be included between the method name and arguments as this
interferes with the Python \texttt{split} method for extracting the fields. The
\texttt{topic} is the string described previously, the \texttt{method} is the
name of the desired method to be called on the agent object, and \texttt{args}
is the arguments supplied to the desired method. In order to send a message to
an agent, the \texttt{publish} method defined in the \texttt{pubsub} module
should be called. An optional argument titled \texttt{cycleCount} is available
which will allow the publish message to be sent multiple times. During testing,
it was found that during the transmission of some messages, this was necessary
due to the way ZeroMQ is implemented.

@@

\subsection{Control Agent Functionality}
The flow chart of method \texttt{setDeviceStatus} is shown in
Figure~\ref{fig:setDeviceStatus}. The purpose of this method is to set the
status of the desired device. When the method is called, the data dictionary is
obtained which contains the device ID. With this device ID, the API type can be
determined using the SQLite database. Subsequently, the appropriate device API
module can be imported. If the power state exists as a key in the device data
dictionary, the power state of the WeMo Insight Switch will be set as ON or OFF.
If the duty cycle key exists, the duty cycle of the single board computer motor
drivers is set. If the shutdown key is set, the single board computer is
shutdown. In order to reconnect to the single board computer, the board must be
started and receiver program ran. If necessary, the device must be reconnected
to the WiFi network. %
%
\begin{figure}
    \centering
    \includegraphics[scale=0.5]{figs/setDeviceStatus.pdf}
    \caption{setDeviceStatus Flow Chart}
    \label{fig:setDeviceStatus}
\end{figure}
%
\todo[inline]{Figures are not cited in the text}

To obtain necessary data quantities from the device, the
\texttt{getDeviceStatus} method is defined. Once the proper data parameters are
obtained, the \texttt{getState} function defined in the devices API module can
be called with the data parameters \replace{like}{, such as} power state and
status. Once the agent has finished sending these to the device, a request is
sent to the web server to inform the server that it completed searching for the
required device data. %

%
\begin{figure}
    \centering
    \includegraphics[scale=0.5]{figs/getDeviceStatus.pdf}
    \caption{getDeviceStatus Flow Chart}
    \label{fig:getDeviceStatus}
\end{figure}
